The {TestIdeals} package for \emph{Macaulay2}

### 2019-04-28 Fsing/TestIdealsPaper/TestIdeals.tex
More changes in examples of paper

i3 : u = f^(5-1);

@@

i7 : u = f^(7-1);

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
i2 : isFInjective R
o2 = true
i3 : R = ZZ/5[x,y,z]/(x^3 + y^3 + z^3);
i4 : isFInjective R
o4 = false
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^5 + (y + 1)^5 + z^5);
i2 : isFInjective R -- R is not globally F-injective...
o2 = false
i3 : isFInjective(R, IsLocal => true) -- but is F-injective at the origin
o3 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
i2 : isFRegular R
o2 = true
i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
i4 : isFRegular R
o4 = false
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y];
i2 : f = y^2 - x^3;
i3 : isFRegular(1/2, f)
o3 = true
i4 : isFRegular(5/6, f)
o4 = false
i5 : isFRegular(4/5, f)
o5 = false
i6 : isFRegular(4/5 - 1/100000, f)
o6 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^3 + (y + 1)^3 + z^3);
i2 : isFRegular R -- R is not globally F-regular...
o2 = false
i3 : isFRegular(R, IsLocal => true) -- but is F-regular at the origin
o3 = true
i4 : R = ZZ/13[x,y];
i5 : f = (y - 2)^2 - (x - 3)^3;
i6 : isFRegular(5/6, f) -- (R,f^(5/6)) is not F-regular...
o6 = false
i7 : isFRegular(5/6, f, IsLocal => true) -- but is F-regular at the origin
o7 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);
i2 : isFPure R
o2 = true
i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);
i4 : isFPure R
o4 = true
i5 : S = ZZ/2[x,y,z];
i5 : isFPure ideal(y^2 - x^3)
o5 = false
i6 : isFPure ideal(z^2 - x*y*z + x*y^2 + x^2*y)
o6 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : S = ZZ/3[a,b,c,d,t];
i2 : m = 4;
i3 : n = 3;
i4 : M = matrix{{ a^2 + t^m, b, d }, { c, a^2, b^n - d }};
i5 : I = minors(2, M);
i6 : R = S/I;
i7 : isFRational R
o7 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^4 + y^4 + z^4);
i2 : N = testModule R;
i3 : N#0
             2             2        2
o3 = ideal (z , y*z, x*z, y , x*y, x )
o3 : Ideal of R
i4 : N#1
o4 = ideal 1
o4 : Ideal of R
\end{MyVerbatim}
}\medskip

The output of \texttt{testModule} is a list, consisting of three items:
\begin{enumerate}[(1)]
\item The test module itself, given as an ideal of $R$.
\item The canonical module that contains the test module, given as an ideal of $R$.  (Note the representation of the canonical module as an ideal is not unique, it is only unique up to isomorphism, hence it is important to return this module as well).
\item The element $u$ described above (not displayed above, since it takes a lot of space).
\end{enumerate}

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(y*z, x*z, x*y);
i2 : N = testModule R;
i3 : N#0
             2   2   2
o3 = ideal (z , y , x )
o3 : Ideal of R
i4 : N#1
o4 = ideal (y - z, x + z)
o4 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : R = ZZ/2[a..e];
i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};
             2       4
o2 : Matrix R  <--- R
i3 : I = minors(2, E);
o3 : Ideal of R
i4 : S = R/I;
i5 : J = parameterTestIdeal S
o5 = ideal (c + d, b, a)
o5 : Ideal of S
i6 : J = substitute(J, R);
o6 : Ideal of R
i7 : mingens(J + I)
o7 = | c+d b a de |
             1       4
o7 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i1 : T = ZZ/7[x,y];
i2 : S = ZZ/7[a,b,c,d];
i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});
i4 : I = ker f;
i5 : R = S/I;
i6 : testIdeal R
o6 = ideal 1
o6 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small
\begin{MyVerbatim}
i7 : toString QGorensteinGenerator(1, R)
o7 = a^2*b^6*c^12+a^3*b^4*c^13+a^3*b^5*c^11*d+a^4*b^3*c^12*d+a^5*b*c^13*d+b^
     12*c^6*d^2+a^3*b^6*c^9*d^2+a^4*b^4*c^10*d^2+a^5*b^2*c^11*d^2+a^6*c^12*d
     ^2+b^13*c^4*d^3+a*b^11*c^5*d^3+a^2*b^9*c^6*d^3+a^4*b^5*c^8*d^3+a^5*b^3*
     c^9*d^3+a^6*b*c^10*d^3+a*b^12*c^3*d^4+a^2*b^10*c^4*d^4+a^3*b^8*c^5*d^4+
     a^4*b^6*c^6*d^4+a^5*b^4*c^7*d^4+a^6*b^2*c^8*d^4+a^7*c^9*d^4+a*b^13*c*d^
     5+a^2*b^11*c^2*d^5+a^3*b^9*c^3*d^5+a^4*b^7*c^4*d^5+a^5*b^5*c^5*d^5+a^6*
     b^3*c^6*d^5+a^7*b*c^7*d^5+a^2*b^12*d^6+a^3*b^10*c*d^6+a^4*b^8*c^2*d^6+a
     ^5*b^6*c^3*d^6+a^6*b^4*c^4*d^6+a^7*b^2*c^5*d^6+a^8*c^6*d^6+a^4*b^9*d^7+
     a^5*b^7*c*d^7+a^6*b^5*c^2*d^7+a^7*b^3*c^3*d^7+a^8*b*c^4*d^7+a^6*b^6*d^8
     +a^7*b^4*c*d^8+a^8*b^2*c^2*d^8+a^9*c^3*d^8+a^8*b^3*d^9+a^9*b*c*d^9+a^10
     *d^10
\end{MyVerbatim}
}\medskip

>>>>

i3 : u = f^(5 - 1);

@@

i7 : u = f^(7 - 1);

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);

i2 : isFInjective R

o2 = true

i3 : R = ZZ/5[x,y,z]/(x^3 + y^3 + z^3);

i4 : isFInjective R

o4 = false
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^5 + (y + 1)^5 + z^5);

i2 : isFInjective R -- R is not globally F-injective...

o2 = false

i3 : isFInjective(R, IsLocal => true) -- but is F-injective at the origin

o3 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);

i2 : isFRegular R

o2 = true

i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);

i4 : isFRegular R

o4 = false
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y];

i2 : f = y^2 - x^3;

i3 : isFRegular(1/2, f)

o3 = true

i4 : isFRegular(5/6, f)

o4 = false

i5 : isFRegular(4/5, f)

o5 = false

i6 : isFRegular(4/5 - 1/100000, f)

o6 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/7[x,y,z]/((x - 1)^3 + (y + 1)^3 + z^3);

i2 : isFRegular R -- R is not globally F-regular...

o2 = false

i3 : isFRegular(R, IsLocal => true) -- but is F-regular at the origin

o3 = true

i4 : R = ZZ/13[x,y];

i5 : f = (y - 2)^2 - (x - 3)^3;

i6 : isFRegular(5/6, f) -- (R,f^(5/6)) is not F-regular...

o6 = false

i7 : isFRegular(5/6, f, IsLocal => true) -- but is F-regular at the origin

o7 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^2 + y*z);

i2 : isFPure R

o2 = true

i3 : R = ZZ/7[x,y,z]/(x^3 + y^3 + z^3);

i4 : isFPure R

o4 = true

i5 : S = ZZ/2[x,y,z];

i5 : isFPure ideal(y^2 - x^3)

o5 = false

i6 : isFPure ideal(z^2 - x*y*z + x*y^2 + x^2*y)

o6 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : S = ZZ/3[a,b,c,d,t];

i2 : M = matrix{{ a^2 + t^4, b, d }, { c, a^2, b^3 - d }};

             2       3
o2 : Matrix S  <--- S

i3 : I = minors(2, M);

o3 : Ideal of S

i4 : R = S/I;

i5 : isFRational R

o5 = true
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(x^4 + y^4 + z^4);

i2 : N = testModule R;

i3 : N#0

             2             2        2
o3 = ideal (z , y*z, x*z, y , x*y, x )

o3 : Ideal of R

i4 : N#1

o4 = ideal 1

o4 : Ideal of R
\end{MyVerbatim}
}\medskip

The output of \texttt{testModule} is a sequence, consisting of three items:
\begin{enumerate}[(1)]
\item The test module itself, given as an ideal of $R$.
\item The canonical module that contains the test module, given as an ideal of $R$.  (Note the representation of the canonical module as an ideal is not unique, it is only unique up to isomorphism, hence it is important to return this module as well).
\item The element $u$ described above (not displayed above, since it takes a lot of space).
\end{enumerate}

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/5[x,y,z]/(y*z, x*z, x*y);

i2 : N = testModule R;

i3 : N#0

             2   2   2
o3 = ideal (z , y , x )

o3 : Ideal of R

i4 : N#1

o4 = ideal (y + 2z, x - z)

o4 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : R = ZZ/2[a..e];

i2 : E = matrix {{a, b, b, e}, {d, d, c, a}};

             2       4
o2 : Matrix R  <--- R

i3 : I = minors(2, E);

o3 : Ideal of R

i4 : S = R/I;

i5 : J = parameterTestIdeal S

o5 = ideal (c + d, b, a)

o5 : Ideal of S

i6 : J = substitute(J, R);

i7 : mingens(J + I)

o7 = | c+d b a de |

             1       4
o7 : Matrix R  <--- R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i1 : T = ZZ/7[x,y];

i2 : S = ZZ/7[a,b,c,d];

i3 : f = map(T, S, {x^3, x^2*y, x*y^2, y^3});

i4 : I = ker f;

i5 : R = S/I;

i6 : testIdeal R

o6 = ideal 1

o6 : Ideal of R
\end{MyVerbatim}
}\medskip

@@

\medskip
{\small\setstretch{.7}
\begin{MyVerbatim}
i7 : toString QGorensteinGenerator(1, R)

o7 = a^2*b^6*c^12+a^3*b^4*c^13+a^3*b^5*c^11*d+a^4*b^3*c^12*d+a^5*b*c^13*d+b^
     12*c^6*d^2+a^3*b^6*c^9*d^2+a^4*b^4*c^10*d^2+a^5*b^2*c^11*d^2+a^6*c^12*d
     ^2+b^13*c^4*d^3+a*b^11*c^5*d^3+a^2*b^9*c^6*d^3+a^4*b^5*c^8*d^3+a^5*b^3*
     c^9*d^3+a^6*b*c^10*d^3+a*b^12*c^3*d^4+a^2*b^10*c^4*d^4+a^3*b^8*c^5*d^4+
     a^4*b^6*c^6*d^4+a^5*b^4*c^7*d^4+a^6*b^2*c^8*d^4+a^7*c^9*d^4+a*b^13*c*d^
     5+a^2*b^11*c^2*d^5+a^3*b^9*c^3*d^5+a^4*b^7*c^4*d^5+a^5*b^5*c^5*d^5+a^6*
     b^3*c^6*d^5+a^7*b*c^7*d^5+a^2*b^12*d^6+a^3*b^10*c*d^6+a^4*b^8*c^2*d^6+a
     ^5*b^6*c^3*d^6+a^6*b^4*c^4*d^6+a^7*b^2*c^5*d^6+a^8*c^6*d^6+a^4*b^9*d^7+
     a^5*b^7*c*d^7+a^6*b^5*c^2*d^7+a^7*b^3*c^3*d^7+a^8*b*c^4*d^7+a^6*b^6*d^8
     +a^7*b^4*c*d^8+a^8*b^2*c^2*d^8+a^9*c^3*d^8+a^8*b^3*d^9+a^9*b*c*d^9+a^10
     *d^10
\end{MyVerbatim}
}\medskip
